Weather Data Integration and Assimilation System\\

### 2020-02-09 introduction/sec_2-problem_and_objectives.tex
Merged problem and objectives

>>>>

\section{Objectives}
\db{We address above problem statement by  achieving the following objectives:}
\begin{itemize}
    \item To develop an open platform to integrate weather data from different sources in different formats
    \item To design and develop a schema to store multidimensional weather timeseries data while optimizing access time, availability, and storage.
    \item To optimize schema to support data queries based on geography and time
    \item To develop an API to share data while providing role-based access control
\end{itemize}
